Article 1 : Pathway found for treatment-resistant lung cancer

### 2019-10-23 _posts/2019-09-18-article-1/article-1.Rmd
categories (2eme essai)

---
title: "Article 1 : Pathway found for treatment-resistant lung cancer"
author:
  - name: Aurélie Pinchart
date: 10-11-2019
categories:
  - track
preview: 
output:
  distill::distill_article:
    self_contained: false
---

>>>>

---
title: "Article 1 : Pathway found for treatment-resistant lung cancer"
author:
  - name: Aurélie Pinchart
date: 10-11-2019
categories:
  - apoptosis
  - TMP-1
  - IL-6
preview: 
output:
  distill::distill_article:
    self_contained: false
---
